\thesistitle

### 2019-07-24 sections/background.tex
Table stuff

\section{Code clone terminology}\label{sec:terminology}
Many studies present different definitions for code clone concepts. For this study, we mainly use the definitions from Bruntink et al. \cite{bruntink2005use}, Roy et al. \cite{roy2007survey} and Jiang et al. \cite{jiang2007deckard}. We created a summary of these concepts, which can be found in table \ref{tab:clone-terminology}.

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}llll@{}}
\toprule
\rowcolor[HTML]{FFFFFF}
\textbf{Symbol} & \textbf{Meaning} & \textbf{Description} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & \textbf{Clones:} Set of clone classes. \\
\rowcolor[HTML]{FFFFFF}
C & Clone class & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.\end{tabular} & \textbf{Instances:} Set of clone instances. \\
\rowcolor[HTML]{EFEFEF}
I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Contents:} Totally ordered set of nodes, ordered\\by their begin positions.\\ \textbf{File:} The file in which this clone instance is \\ found.\\ \textbf{Range:} The range this clone instance spans.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
N & Node & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \textbf{Range:} The range this node spans. \\
\rowcolor[HTML]{EFEFEF}
R & Range & A part of a source code file. & \begin{tabular}[c]{@{}l@{}}\textbf{Tokens:} Set of tokens that this range spans.\\ \textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
T & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token spans.\\ \textbf{Category:} Identifier, Keyword, Literal, Separator, \\ Operator, Comment or Whitespace\end{tabular} \\ \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}

>>>>

\section{Code clone terminology}\label{sec:terminology}
% The sets are actually definitions, NOT PROPERTIES. This should be clearer.
Many studies present different definitions for code clone concepts. For this study, we mainly use the definitions from Bruntink et al. \cite{bruntink2005use}, Roy et al. \cite{roy2007survey} and Jiang et al. \cite{jiang2007deckard}. We created a summary of these concepts, which can be found in table \ref{tab:clone-terminology}.

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
\rowcolor[HTML]{FFFFFF}
\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone classes.\\$S=\{C_1, C_2, ...\}$\end{tabular} &  & - \\
\rowcolor[HTML]{FFFFFF}
C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations. Each of these code fragments\\is called a ``clone instance''.\end{tabular} &  & - \\
\rowcolor[HTML]{EFEFEF}
I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} &  & \begin{tabular}[c]{@{}l@{}}\textbf{File:} The file in which this clone instance is \\ found.\\ \textbf{Range:} The range this clone instance spans.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
N & Node \ref{jiang2007deckard}& \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} &  & \textbf{Range:} The range this node spans. \\
\rowcolor[HTML]{EFEFEF}
T & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} &  & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token spans.\\ \textbf{Category:} Identifier, Keyword, Literal, Separator, \\ Operator, Comment or Whitespace\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
R & Range & A part of a source code file. &  & \begin{tabular}[c]{@{}l@{}}\textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
 \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}
